Scaling through abstractions – high-performance vectorial wave simulations for seismic inversion with Devito

### 2020-06-01 paper.tex
add refs and FIXME

We here provide a succinct description of distributed-memory parallelism
in Devito; the interested reader should refer to the MPI tutorial at
\href{https://github.com/devitocodes/devito/blob/v4.2/examples/mpi/overview.ipynb}{mpi-notebook}
for thorough explanations and practical examples.
\textcolor{red}{We highlugh the main feature of the distributed framework tha enable the industry scale
applications we describe in this paper. A more thorough study of its implementation, including `mpi4numpy' and
a complete scaling analysis will be presented in a later paper. Initial results assciated with early version of \devito's
distributed computing capabilities can be found in \cite{luporini2019adp} on a conventional cluster and 
in \cite{witte2019ecl} that contains results on AWS.}

>>>>

We here provide a succinct description of distributed-memory parallelism
in Devito; the interested reader should refer to the MPI tutorial at
\href{https://github.com/devitocodes/devito/blob/v4.2/examples/mpi/overview.ipynb}{mpi-notebook}
for thorough explanations and practical examples.
